Simulation of Congenital Heart Defect Corrective Surgeries Using Thin Shell Elements

### 2012-03-01 Doc/Miccai/conclusion.tex
Updated style.
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@376 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

We introduced a new approach for predictive simulation of CHD corrective surgeries. It is based on thin shell elements and a relaxation method for joining of blood vessels and patches by topologically connecting the vertices of joining edges of the simulation meshes. All necessary low-level surgical procedures can be performed using this method. We showed that we need only a small number of thin shell elemenets to achieve physically accurat simulation results which enable fast simulations. Special care has to be taken during initial mesh generation and dynamic remeshing when cutting blood vessels since the size of newly generated thin shell elements should roughly equal the size of their neighbor elements which is a common constraint for finite element simulations. To truly benefit from our simulation approach, future work has to be done in terms of remeshing, to keep a high quality of the mesh during the whole simulation.

>>>>

We introduced a new approach for predictive simulation of CHD corrective surgeries. It is based on thin shell elements and a relaxation method for joining of blood vessels and patches by topologically connecting the vertices of joining edges of the simulation meshes. All necessary low-level surgical procedures can be performed using this method. We showed that we need only a small number of thin shell elemenets to achieve physically accurat simulation results which enable fast simulations. Special care has to be taken during initial mesh generation and dynamic remeshing when cutting blood vessels since the size of newly generated thin shell elements should roughly equal the size of their neighbor elements which is a common constraint for finite element simulations. To truly benefit from our simulation approach, future work has to be done in terms of remeshing, to keep a high quality of the mesh during the simulation.
